\textit{Supplemental figures for}: A Gaussian process model of human electrocorticographic data

### 2020-03-11 paper/main.tex
implemented overline suggestion from tudor

\begin{figure}
  \centering \includegraphics[width=\textwidth]{figs/methods}
  \caption{\textbf{Methods overview.}  \textbf{A.~Electrode locations.}  Each
  dot reflects the location of a single electrode implanted in the brain of a
  Dataset 1 patient.  A held-out recording location from one patient is
  indicated in red, and the patient's remaining electrodes are indicated in
  black. The electrodes from the remaining patients are colored by $k$-means
  cluster (computed using the full-brain correlation model shown in Panel D).
  \textbf{B.~Radial basis function kernel.} Each electrode contributed by the
  patient (black) weights on the full set of locations under consideration (all
  dots in Panel A, defined as $\bar{R}$ in the text).  The weights fall off with
  positional distance (in MNI152 space) according to an RBF. \textbf{C.~Per-patient
  correlation matrices.}  After computing the pairwise correlations between the
  recordings from each patient's electrodes, we use RBF-weighted averages to
  estimate correlations between all locations in $\bar{R}$.  We obtain an
  estimated full-brain correlation matrix using each patient's data.
  \textbf{D.~Merged correlation model.}  We combine the per-patient correlation
  matrices (Panel C) to obtain a single full-brain correlation model that
  captures information contributed by every patient.  Here we have sorted the
  rows and columns to reflect $k$-means clustering labels~\citep[using
  $k$=7;][]{YeoEtal11}, whereby we grouped locations based on their correlations
  with the rest of the brain (i.e., rows of the matrix displayed in the panel).
  The boundaries denote the cluster groups.  The rows and columns of Panel C
  have been sorted using the Panel D-derived cluster labels.
  \textbf{E.~Reconstructing activity throughout the brain.}  Given the observed
  recordings from the given patient (shown in black; held-out recording is shown
  in blue), along with a full-brain correlation model (Panel D), we use
  Equation~\ref{eqn:reconstruction} to reconstruct the most probable activity at
  the held-out location (red).} \label{fig:methods}
\end{figure}

@@

A second mechanism whereby a given region $x$ can contribute to the recording at
$\eta$ is through (direct or indirect) anatomical connections between structures
near $x$ and $\eta$.  Although anatomical and functional correlations can differ
markedly~\citep[e.g.,][]{AdacEtal12, HoneEtal09, GoniEtal14}, we use temporal
correlations in the data to estimate these anatomical
connections~\citep{BeckEtal18}.  Let $\bar{R}$ be the set of locations at which
we wish to estimate local field potentials, and let $R_{s} \subseteq \bar{R}$ be
set of locations at which we observe local field potentials from patient $s$
(excluding the electrodes that did not pass the kurtosis test described above).
In the analyses below we define $\bar{R} = \cup_{s=1}^S R_s$.  We can calculate
the expected inter-electrode correlation matrix for patient $s$, where
$C_{s,k}(i,j)$ is the correlation between the time series of voltages for
electrodes $i$ and $j$ from subject $s$ during session $k$, using:

\begin{align}
  \bar{C}_{s} &=
  \mathrm{r}\left(\frac{1}{n}\left(\sum_{k=1}^{n}\mathrm{z}(C_{s,k})\right)\right),\label{eqn:inter_corr}~\mathrm{where}\\
  \mathrm{z}(r) &= \frac{\log(1+r) - \log(1 - r)}{2}~\mathrm{is~the~Fisher}~z
  \mathrm{-transformation~and}\label{eqn:fishersz}\\ \mathrm{z}^{-1}(z) =
  \mathrm{r}(z) &= \frac{\exp(2z) - 1}{\exp(2z) +
  1}\mathrm{~is~its~inverse}.\label{eqn:invfishersz} \end{align} Next, we use
  Equation~\ref{eqn:rbf} to construct a number of to-be-estimated locations by
  number of patient electrode locations weight matrix, $W_s$.  Specifically,
  $W_s$ approximates how informative the recordings at each location in $R_s$
  are in reconstructing activity at each location in $\bar{R}$, where the
  contributions fall off with an RBF according to the distances between the
  corresponding locations:

@@

Given this weight matrix, $W_s$, and the observed inter-electrode correlation
matrix for patient $s$, $\bar{C}_{s}$, we can estimate the correlation matrix
for all locations in $\bar{R}$ ($\hat{C}_s$; Fig.~\ref{fig:methods}C) using:

\begin{align}
\hat{N}_{s}(x,y) & = { \sum_{i = 1}^{| R_{s}|}\sum_{j=1}^{i-1} W(x,i) \cdot W(y,j)\cdot \mathrm{z}(\bar{C}_{s}(i,j))}\label{eqn:subj_corrmat_num}\\
 \hat{D}_{s}(x,y) & = \sum_{i = 1}^{| R_{s}|}\sum_{j=1}^{i-1} W(x,i)
                    \cdot W(y,j). \label{eqn:subj_corrmat_den}\\
 \hat{C}_s &= \mathrm{r}\left( \frac{\hat{N}_{s}}{\hat{D}_{s}} \right)
             \label{eqn:subj_corrmat}.
\end{align}
After estimating the numerator ($\hat{N}_{s}$) and denominator
($\hat{D}_{s}$) placeholders for each $\hat{C}_{s}$, we aggregate these
estimates across the $S$ patients to obtain a single expected full-brain
correlation matrix ($\hat{K}$; Fig.~\ref{fig:methods}D):
\begin{align}
 \hat{K} = \mathrm{r} \left(  \frac{\sum_{s=1}^S  \hat{N}_{s}}{\sum_{s=1}^S \hat{D}_{s}}\right).\label{eqn:corrmat}
\end{align}
Intuitively, the numerators capture the general structures of the
patient-specific estimates of full-brain correlations, and the
denominators account for which locations were near the implanted
electrodes in each patient.  To obtain $\hat{K}$, we compute a
weighted average across the estimated patient-specific full-brain
correlation matrices, where patients with observed electrodes near a
particular set of locations in $\hat{K}$ contribute more to the
estimate.

Having used the multi-patient data to estimate a full-brain correlation matrix
at the set of locations in $\bar{R}$ that we wish to know about, we next use
$\hat{K}$ to estimate activity patterns everywhere in $\bar{R}$, given
observations at only a subset of locations in $\bar{R}$
(Fig.~\ref{fig:methods}E).

Let $\alpha_s$ be the set of indices of patient $s$'s electrode locations in
$\bar{R}$ (i.e., the locations in $R_s$), and let $\beta_s$ be the set of
indices of all other locations in $\bar{R}$. In other words, $\beta_s$ reflects
the locations in $\bar{R}$ where we did not observe a recording for patient $s$
(these are the recording locations we will want to fill in using SuperEEG). We
can sub-divide $\hat{K}$ as follows:

@@

\begin{align}
\hat{Y}_{s,k,\beta_s} &= ((\hat{K}_{\beta_s,\alpha_s}\cdot\hat{K}_{\alpha_s,\alpha_s}^{-1})\cdot Y_{s,k,\alpha_s}^\mathrm{T})^\mathrm{T}.\label{eqn:reconstruction}
\end{align}
This equation is the foundation of the SuperEEG algorithm.  Whereas we
observe recordings only at the locations indexed by $\alpha_s$,
Equation~\ref{eqn:reconstruction} allows us to estimate the recordings
at all locations indexed by $\beta_s$, which we can define \textit{a priori}
to include any locations we wish, throughout the brain.  This yields
estimates of the time-varying voltages at \textit{every} location in
$\bar{R}$, provided that we define $\bar{R}$ in advance to include the
union of all of the locations in $R_s$ and all of the locations
at which we wish to estimate recordings (i.e., a timeseries of
voltages).

@@

The SuperEEG algorithm described above and in Figure~\ref{fig:methods} allows us
to estimate, up to a constant scaling factor, local field potentials (LFPs) for
each patient at all arbitrarily chosen locations in the set $\bar{R}$,
\textit{even if we did not record that patient's brain at all of those
locations}.  We next turn to an evaluation of the accuracy of those estimates.

@@

We used this general approach to quantify the algorithm's performance across the
full dataset. For each held-out electrode, from each held-out patient in turn,
we computed the average correlation (across recording sessions) between the
SuperEEG-reconstructed voltage traces and the observed voltage traces from that
electrode.  For this analysis we set $\bar{R}$ to be the union of all electrode
locations across all patients.  This yielded a single correlation coefficient
for each electrode location in $\bar{R}$, reflecting how well the SuperEEG
algorithm was able to recover the recording at that location by incorporating
data across patients (black histogram in Fig.~\ref{fig:corrmap}A, map in
Fig.~\ref{fig:corrmap}C).  The observed distribution of correlations was
centered well above zero (mean: $r = 0.51$; $t$-test comparing mean of distribution of
$z$-transformed average patient correlation coefficients to 0: $t(66) = 23.55, p
< 10^{-10}$), indicating that the SuperEEG algorithm recovers held-out activity
patterns substantially better than random guessing.

>>>>

\begin{figure}
  \centering \includegraphics[width=\textwidth]{figs/methods}
  \caption{\textbf{Methods overview.}  \textbf{A.~Electrode locations.}  Each
  dot reflects the location of a single electrode implanted in the brain of a
  Dataset 1 patient.  A held-out recording location from one patient is
  indicated in red, and the patient's remaining electrodes are indicated in
  black. The electrodes from the remaining patients are colored by $k$-means
  cluster (computed using the full-brain correlation model shown in Panel D).
  \textbf{B.~Radial basis function kernel.} Each electrode contributed by the
  patient (black) weights on the full set of locations under consideration (all
  dots in Panel A, defined as $\overline{R}$ in the text).  The weights fall off with
  positional distance (in MNI152 space) according to an RBF. \textbf{C.~Per-patient
  correlation matrices.}  After computing the pairwise correlations between the
  recordings from each patient's electrodes, we use RBF-weighted averages to
  estimate correlations between all locations in $\overline{R}$.  We obtain an
  estimated full-brain correlation matrix using each patient's data.
  \textbf{D.~Merged correlation model.}  We combine the per-patient correlation
  matrices (Panel C) to obtain a single full-brain correlation model that
  captures information contributed by every patient.  Here we have sorted the
  rows and columns to reflect $k$-means clustering labels~\citep[using
  $k$=7;][]{YeoEtal11}, whereby we grouped locations based on their correlations
  with the rest of the brain (i.e., rows of the matrix displayed in the panel).
  The boundaries denote the cluster groups.  The rows and columns of Panel C
  have been sorted using the Panel D-derived cluster labels.
  \textbf{E.~Reconstructing activity throughout the brain.}  Given the observed
  recordings from the given patient (shown in black; held-out recording is shown
  in blue), along with a full-brain correlation model (Panel D), we use
  Equation~\ref{eqn:reconstruction} to reconstruct the most probable activity at
  the held-out location (red).} \label{fig:methods}
\end{figure}

@@

A second mechanism whereby a given region $x$ can contribute to the recording at
$\eta$ is through (direct or indirect) anatomical connections between structures
near $x$ and $\eta$.  Although anatomical and functional correlations can differ
markedly~\citep[e.g.,][]{AdacEtal12, HoneEtal09, GoniEtal14}, we use temporal
correlations in the data to estimate these anatomical
connections~\citep{BeckEtal18}.  Let $\overline{R}$ be the set of locations at which
we wish to estimate local field potentials, and let $R_{s} \subseteq \overline{R}$ be
set of locations at which we observe local field potentials from patient $s$
(excluding the electrodes that did not pass the kurtosis test described above).
In the analyses below we define $\overline{R} = \cup_{s=1}^S R_s$.  We can calculate
the expected inter-electrode correlation matrix for patient $s$, where
$C_{s,k}(i,j)$ is the correlation between the time series of voltages for
electrodes $i$ and $j$ from subject $s$ during session $k$, using:

\begin{align}
  \overline{C}_{s} &=
  \mathrm{r}\left(\frac{1}{n}\left(\sum_{k=1}^{n}\mathrm{z}(C_{s,k})\right)\right),\label{eqn:inter_corr}~\mathrm{where}\\
  \mathrm{z}(r) &= \frac{\log(1+r) - \log(1 - r)}{2}~\mathrm{is~the~Fisher}~z
  \mathrm{-transformation~and}\label{eqn:fishersz}\\ \mathrm{z}^{-1}(z) =
  \mathrm{r}(z) &= \frac{\exp(2z) - 1}{\exp(2z) +
  1}\mathrm{~is~its~inverse}.\label{eqn:invfishersz} \end{align} Next, we use
  Equation~\ref{eqn:rbf} to construct a number of to-be-estimated locations by
  number of patient electrode locations weight matrix, $W_s$.  Specifically,
  $W_s$ approximates how informative the recordings at each location in $R_s$
  are in reconstructing activity at each location in $\overline{R}$, where the
  contributions fall off with an RBF according to the distances between the
  corresponding locations:

@@

Given this weight matrix, $W_s$, and the observed inter-electrode correlation
matrix for patient $s$, $\overline{C}_{s}$, we can estimate the correlation matrix
for all locations in $\overline{R}$ ($\hat{C}_s$; Fig.~\ref{fig:methods}C) using:

\begin{align}
\hat{N}_{s}(x,y) & = { \sum_{i = 1}^{| R_{s}|}\sum_{j=1}^{i-1} W(x,i) \cdot W(y,j)\cdot \mathrm{z}(\overline{C}_{s}(i,j))}\label{eqn:subj_corrmat_num}\\
 \hat{D}_{s}(x,y) & = \sum_{i = 1}^{| R_{s}|}\sum_{j=1}^{i-1} W(x,i)
                    \cdot W(y,j). \label{eqn:subj_corrmat_den}\\
 \hat{C}_s &= \mathrm{r}\left( \frac{\hat{N}_{s}}{\hat{D}_{s}} \right)
             \label{eqn:subj_corrmat}.
\end{align}
After estimating the numerator ($\hat{N}_{s}$) and denominator
($\hat{D}_{s}$) placeholders for each $\hat{C}_{s}$, we aggregate these
estimates across the $S$ patients to obtain a single expected full-brain
correlation matrix ($\hat{K}$; Fig.~\ref{fig:methods}D):
\begin{align}
 \hat{K} = \mathrm{r} \left(  \frac{\sum_{s=1}^S  \hat{N}_{s}}{\sum_{s=1}^S \hat{D}_{s}}\right).\label{eqn:corrmat}
\end{align}
Intuitively, the numerators capture the general structures of the
patient-specific estimates of full-brain correlations, and the
denominators account for which locations were near the implanted
electrodes in each patient.  To obtain $\hat{K}$, we compute a
weighted average across the estimated patient-specific full-brain
correlation matrices, where patients with observed electrodes near a
particular set of locations in $\hat{K}$ contribute more to the
estimate.

Having used the multi-patient data to estimate a full-brain correlation matrix
at the set of locations in $\overline{R}$ that we wish to know about, we next use
$\hat{K}$ to estimate activity patterns everywhere in $\overline{R}$, given
observations at only a subset of locations in $\overline{R}$
(Fig.~\ref{fig:methods}E).

Let $\alpha_s$ be the set of indices of patient $s$'s electrode locations in
$\overline{R}$ (i.e., the locations in $R_s$), and let $\beta_s$ be the set of
indices of all other locations in $\overline{R}$. In other words, $\beta_s$ reflects
the locations in $\overline{R}$ where we did not observe a recording for patient $s$
(these are the recording locations we will want to fill in using SuperEEG). We
can sub-divide $\hat{K}$ as follows:

@@

\begin{align}
\hat{Y}_{s,k,\beta_s} &= ((\hat{K}_{\beta_s,\alpha_s}\cdot\hat{K}_{\alpha_s,\alpha_s}^{-1})\cdot Y_{s,k,\alpha_s}^\mathrm{T})^\mathrm{T}.\label{eqn:reconstruction}
\end{align}
This equation is the foundation of the SuperEEG algorithm.  Whereas we
observe recordings only at the locations indexed by $\alpha_s$,
Equation~\ref{eqn:reconstruction} allows us to estimate the recordings
at all locations indexed by $\beta_s$, which we can define \textit{a priori}
to include any locations we wish, throughout the brain.  This yields
estimates of the time-varying voltages at \textit{every} location in
$\overline{R}$, provided that we define $\overline{R}$ in advance to include the
union of all of the locations in $R_s$ and all of the locations
at which we wish to estimate recordings (i.e., a timeseries of
voltages).

@@

The SuperEEG algorithm described above and in Figure~\ref{fig:methods} allows us
to estimate, up to a constant scaling factor, local field potentials (LFPs) for
each patient at all arbitrarily chosen locations in the set $\overline{R}$,
\textit{even if we did not record that patient's brain at all of those
locations}.  We next turn to an evaluation of the accuracy of those estimates.

@@

We used this general approach to quantify the algorithm's performance across the
full dataset. For each held-out electrode, from each held-out patient in turn,
we computed the average correlation (across recording sessions) between the
SuperEEG-reconstructed voltage traces and the observed voltage traces from that
electrode.  For this analysis we set $\overline{R}$ to be the union of all electrode
locations across all patients.  This yielded a single correlation coefficient
for each electrode location in $\overline{R}$, reflecting how well the SuperEEG
algorithm was able to recover the recording at that location by incorporating
data across patients (black histogram in Fig.~\ref{fig:corrmap}A, map in
Fig.~\ref{fig:corrmap}C).  The observed distribution of correlations was
centered well above zero (mean: $r = 0.51$; $t$-test comparing mean of distribution of
$z$-transformed average patient correlation coefficients to 0: $t(66) = 23.55, p
< 10^{-10}$), indicating that the SuperEEG algorithm recovers held-out activity
patterns substantially better than random guessing.

### 2020-03-11 paper/supporting_information.tex
implemented overline suggestion from tudor

\begin{figure}[p]
\centering \includegraphics[width=\textwidth]{figs/supplemental_8}
\caption{\textbf{Stability of full-brain correlation matrices across
    patients.}  We estimated full-brain correlation matrices
  ($\bar{K}$) using different subsets of patients from each
  dataset. We explored how stable these estimates were as a function
  of how many patients were used to compute $\bar{K}$. For each sample
  size $n$ (number of patients), we drew two non-overlapping sets of
  $n$ patients (without replacement) from the full set of patients in
  each dataset. We then estimated $\bar{K}$ using the two sets of $n$
  patients.  We computed the correlation between the upper triangles
  of these matrices as a measure of how similar the matrices were.  We
  repeated this procedure 500 times for each value of $n$ (ranging
  from 1 up to $\frac{1}{2}$ of the total number of patients in the
  given dataset); this yielded a distribution of correlation
  coefficients for each value of $n$.  Panels \textbf{A} and
  \textbf{C} display the mean correlations as a function of $n$ for
  Datasets 1 and 2, respectively.  The error ribbons denote 95\%
  confidence intervals (computed across iterations).  Panels
  \textbf{B} and \textbf{D} display the standard error of the mean
  (SEM) of these distributions of correlations as a function of $n$,
  for Datasets 1 and 2, respectively.  The error ribbons denote
  bootstrap-derived 95\% confidence intervals.}
\label{fig:supplemental_8}
\end{figure}

>>>>

\begin{figure}[p]
\centering \includegraphics[width=\textwidth]{figs/supplemental_8}
\caption{\textbf{Stability of full-brain correlation matrices across
    patients.}  We estimated full-brain correlation matrices
  ($\overline{K}$) using different subsets of patients from each
  dataset. We explored how stable these estimates were as a function
  of how many patients were used to compute $\overline{K}$. For each sample
  size $n$ (number of patients), we drew two non-overlapping sets of
  $n$ patients (without replacement) from the full set of patients in
  each dataset. We then estimated $\overline{K}$ using the two sets of $n$
  patients.  We computed the correlation between the upper triangles
  of these matrices as a measure of how similar the matrices were.  We
  repeated this procedure 500 times for each value of $n$ (ranging
  from 1 up to $\frac{1}{2}$ of the total number of patients in the
  given dataset); this yielded a distribution of correlation
  coefficients for each value of $n$.  Panels \textbf{A} and
  \textbf{C} display the mean correlations as a function of $n$ for
  Datasets 1 and 2, respectively.  The error ribbons denote 95\%
  confidence intervals (computed across iterations).  Panels
  \textbf{B} and \textbf{D} display the standard error of the mean
  (SEM) of these distributions of correlations as a function of $n$,
  for Datasets 1 and 2, respectively.  The error ribbons denote
  bootstrap-derived 95\% confidence intervals.}
\label{fig:supplemental_8}
\end{figure}
